---
title: "Analysis of Incentives in Sustainable Fashion Brand Communities"
author: "Team 1 - Camila Cordova, Victoria Garcia, Manya Arora"
date: "27/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages, Functions, and Data

```{r results = F, warning=F, message=F}
############### ANALYSIS OF DATA FROM QUALTRICS ###############

library(data.table)
library(tidyverse)
library(dplyr)
library(tidyselect)
if(!require(gridExtra)) install.packages('gridExtra')

##############################        LOAD DATA      ###########################

dt <- fread('Thesis Survey Best case.csv', stringsAsFactors = F, header = T) %>% 
  as_tibble()

```

## Inspect and clean data

See what the table looks like and the column names:

```{r warning=F, message=F}

dt
colnames(dt)

```


### Removing unusable answers

We need to remove the first two lines that are not useful for our analysis, but we will save the first line, because it contains the descriptions of our variables.

```{r warning=F, message=F}

dt_question_labels <- dt %>% slice(1)

dt_question_labels <- dt_question_labels %>% 
  t() %>%
   as.data.frame() %>% 
   mutate(Label = rownames(.))

(dt <- dt %>% 
  slice(-c(1,2)))

```


We also need to remove the answers that were given in "Preview" mode or "Test" mode, because those are not collected from the experimental sample.

```{r eval = F,warning=F, message=F}

dt <- dt %>% 
  filter(!(Status %in% c('Survey Preview', 'Survey Test')))

```

We want to give distinctive names to our questions.

```{r warning=F, message=F}

dt <- dt %>% 
  rename(Participation1a = Q6, Brand_reputation1a = Q7, Brand_reputation1b = Q8, Participation1b = Q15, Commitment1a = Q16, Social_cause_interest_c = Q80, Reward_c = Q81, Theoretical_domain_c = Q82, Social_cause_interest_c2 = Q83, Attention_check_c = Q79, Commitment_c = Q84, Theoretical_domain_c2 = Q87,
         Participation2a = Q21, Brand_reputation2a = Q22, Brand_reputation2b = Q23, Participation2b = Q30, Commitment2a = Q31, Participation2c = Q59,
         Participation3a = Q36, Brand_reputation3a = Q38, Brand_reputation3b = Q39, Participation3b = Q46, Commitment3a = Q47, Participation3c = Q60, Ease_of_use = Q37, Age = Q48, Gender = Q49, Nationality = Q50, Occupation = Q51)

```

Then we need to transform likert scales into numeric vectors.

vars_to_transform <- c('Participation1a',

                      'Participation1b',

                      'Participation2a',

                      'Participation2b',

                      'Participation2c',

                      'Participation3a',

                      'Participation3b',

                      'Participation3c',

                      'Brand_reputation1a',

                      'Brand_reputation1b',

                      'Brand_reputation2a',

                      'Brand_reputation2b',

                      'Brand_reputation3a',

                      'Brand_reputation3b',

                      'Social_cause_interest_c',

                      'Social_cause_interest_c2',

                      'Reward_c',

                      'Attention_check_c',

                      'Commitment_c',

                      'Commitment1a',

                      'Commitment2a',

                      'Commitment3a',

                      'Ease_of_use')

 

dt <- dt %>%

  #First transform empty values into NA

  mutate_all(., function(x) ifelse(x == '', NA, x)) %>%

  #Then make first factor, then numeric

  mutate_at(.vars = all_of(vars_to_transform),

            .funs = function(x) as.numeric(as.factor(x)))
```{r warning=T, message=F}

dt <- dt %>% 
  mutate_at(.vars = c('Participation1a', 'Brand_reputation1a', 'Brand_reputation1b', 'Participation1b', 'Commitment1a', 'Social_cause_interest_c', 'Reward_c', 'Social_cause_interest_c2', 'Attention_check_c', 'Commitment_c',
         'Participation2a', 'Brand_reputation2a', 'Brand_reputation2b', 'Participation2b', 'Commitment2a', 'Participation2c',
         'Participation3a', 'Brand_reputation3a', 'Brand_reputation3b', 'Participation3b', 'Commitment3a', 'Participation3c', 'Ease_of_use'), .funs = as.numeric)

```

### Control variables

You need to transform the interval variables into factors

```{r warning=F, message=F}
dt <- dt %>% 
  mutate_at(c('Age', 'Gender', 'Nationality', 'Occupation'), as.factor) 
```

And the binary variables into 0/1 variables

```{r warning=F, message=F}
dt <- dt %>% 
  mutate(Theoretical_domain_c = ifelse(Theoretical_domain_c == 'Yes', 1, 0))
dt <- dt %>% 
  mutate(Theoretical_domain_c2 = ifelse(Theoretical_domain_c2 == 'Yes', 1, 0))
```

### Treatment variables

We need to add one more variable that indicates in which condition people are assigned. I have 2 treatments and 1 control group in this example. You may have 1 treatment and 1 control, or more treatments and 1 control. You can adjust the code to your case.

```{r warning=F, message=F}
dt <- dt %>% 
  mutate(Condition = ifelse(!is.na(Participation1a), 'S1',
                            ifelse(!is.na(Participation2a), 'S2',ifelse(!is.na(Participation3a),'S3',
                                   'Control'))))

```


### Dependent variable

You measured the DV separately in each block (treatment block and control block.

**Your DV should have no missing values.**

#### Case 1: You measured the DV separately in each block (treatment block and control block).

If you measured the DV in the same block as the treatment, then we need to also add one variable with the value of the DV. 

```{r warning=F, message=F}



dt$DV<- rowMeans(dt %>% select(Participation1a, Participation1b, Participation2a, Participation2b, Participation2c, Participation3a, Participation3b, Participation3c), na.rm = T)


```


## Data Analysis: Unstandardized Betas

### Mean difference without control questions

We want to know if the mean responses in our treatment conditions significantly differ from our control group. We can do this with a regression analysis.

```{r warning=F, message=F}

fit1 <- lm(DV ~ 1 + Condition, data = dt)
summary(fit1)

```

In this example, the people in condition T1 are on average less likely to give higher responses to the DV compared to the control group (beta coefficient is negative). People in condition T2 are on average more likely to give higher responses to the DV compared to the control group (beta coefficient is positive). However, the standard errors are large. Therefore, my effects overlap with zero.


### Mean difference with control questions(I cannot run it without Age, Gender, Nationality and Occupation and we cannot assume any of those for the non responses)

We can also add the control variables and check how our results change.

```{r warning=F, message=F}

fit2 <- lm(DV ~ 1 + Condition + Social_cause_interest_c + Social_cause_interest_c2 + Reward_c + Theoretical_domain_c + Theoretical_domain_c2 + Commitment_c + Age + Gender + tolower(Nationality) + Occupation, data = dt)

summary(fit2)

```

## Data Analysis: Standardized Betas

In order to obtain standardized betas, we need to standardize our input variables. You can standardize all variables that are measured with a numerical scale.

It doesn't help to standardize categorical (discrete) variables, measured with text or labels.

### No control variables

```{r warning=F, message=F}

fit3 <- lm(scale(DV) ~ 1 + Condition, data = dt)

summary(fit3)

```


### With Control Variables


```{r warning=F, message=F}

fit4 <- lm(scale(DV) ~ 1 + Condition + Social_cause_interest_c + Social_cause_interest_c2 + Reward_c + Theoretical_domain_c + Theoretical_domain_c2 + Commitment_c + Age + Gender + tolower(Nationality) + Occupation, data = dt)

summary(fit4)

```
